D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-19 ootavacuous.tex
Explicitly call out mapping of abstract machine onto matter/energy
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Real-world constraints are imposed by the standard, which have been
considered in prior work, and by the laws of physics, which have
not.
Additional constraints are imposed by hardware architecture and
design, which have been partially accounted for in the standard,
one limitation being that accurate and executable formal descriptions
of hardware memory models did not appear until after the standard
was released.
A final set of constraints is imposed by the C++ implementations
themselves.

@@

% @@@ TODO:
% Emphasize that real-world implementations map abstract machine to matter
%	and energy in the real world.

>>>>

Real-world constraints are imposed by the standard, which have been
considered in prior work.
However, in correct real-world C++ implementations, the standard's
abstract machine must be mapped onto real matter and energy.
This mapping has not been considered by prior work, and brings to
bear additional constraints from the laws of physics and from hardware
architecture and design, both of which have been only partially accounted
for in the standard.
One reason for the incomplete accounting for hardware constraints is
that accurate and executable formal descriptions of hardware memory
models did not appear until after the standard was released.
A final set of constraints is imposed by the C++ implementations
themselves, some of which have resulted in non-determinisms within
the standard.\footnote{
	For example, when pre-existing implementations could not agree
	on any specific deterministic handling of side-effects within
	expressions.
	On the other hand, implementer freedom does have significant
	value.}

@@

% @@@ TODO:
